\sysfull

### 2017-08-11 paper/evaluation.tex

Additionally, we evaluated the compile time for automatic task generation per application\footnote{We could not compile the DFT application since LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the apps on a 4-core virtual machine with 1\,GB memory with Arch Linux, running on Intel Core i5-6200U (2.30\,GHz) processor. The result are given in Table~\ref{table:compiler_result}. We used the {\tt time} linux command to measure the rough time. Most of the compile time was due to pointer aliasing, when calculating possible live ranges of variables. Apps such as RSA whose code size is large and uses a lot of variables, need longer compilation time due to a larger search space for pointer aliasing.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coala_chain}
	\caption{Performance of \sys's fixed power and at multiple WISP to RFID reader antenna distances, \{20, 40, 60\}\,cm, compared against Chain.}
	\label{fig:coalescing}
\end{figure}

Experimental evaluation of task coalescing mechanism under intermittent power of \sys is given in Figure~\ref{fig:coalescing}. For each application we measured execution time (with and without task coalescing) at \{20, 40, 60\}\,cm distance between RFID antenna and WISP and when WISP was powered directly from FET. Each measurement was repeated x times per each distance/application. From the result we clearly see an enormous benefit of coalescing, especially at large WISP to RFID reader antenna distance ($\approx$56\% for cem, 100\% for sort and $\approx$400\% for bc). At each distance, \sys coalescing mechanism provided faster execution times compared to the non-coalescing case. \todo{Discuss different shapes per app}{Amjad}

%\begin{figure}
%	\centering
%	\includegraphics[width=\columnwidth]{figures/virtualTaskSize.eps}
%	\caption{Execution time of a dummy application containing twelve empty tasks as a function of coalescing factor. We observe three times improvement from coalescing until four virtual tasks, while we observe a diminishing return from task coalescing beyond four. \todo{Improve the figure: make it narrower, larger font, remove legend, do not capitalize "Task" in X axis, add Y axis label (Execution time (ms))}{Amjad}}
%	\label{fig:virtualTaskSize}
%\end{figure}

%The question remains: does coalescing all program's tasks into a singe virtual task (as the energy becomes fully available, i.e. from energy harvesting to continuous power environment) is the best one? To answer this question we have implemented a simple program composed of $x$ empty tasks. We execute the same program by increasing coalescing factor by one while the device on which the program was executed was running on a stable power supply (refer to Section~\ref{sec:methodology_evaluation} for details). The result is presented in Figure~\ref{fig:virtualTaskSize}. We observe a significant increase in execution time as task are coalescent from one to four (three times execution time improvement). However, as the coalescing increases beyond four, we observe diminishing returns from coalescing in terms of execution time. \todo{Decide whether to place this figure in Evaluation section or leave it here}{Przemek}

>>>>

Additionally, we evaluated the compile time for automatic task generation per application\footnote{We could not compile the DFT application since LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the apps on a 4-core virtual machine with 1\,GB memory with Arch Linux, running on Intel Core i5-6200U (2.30\,GHz) processor. The result are given in Table~\ref{table:compiler_result}. We used the {\tt time} linux command to measure the rough time. Most of the compile time was due to pointer aliasing, when calculating possible live ranges of variables. Apps such as RSA whose code size is large and uses a lot of variables, need longer compilation time due to a larger search space for pointer aliasing. Nonetheless, the compile time is orders of magnitude shorter than manual task splitting by a programmer (in  order of hours). For this reason we believe that \sys complier will be a major step in enabling computing community to enter the intermittent-power domain without big time investments.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coala_chain}
	\caption{Performance of \sys's fixed power and at multiple WISP to RFID reader antenna distances, \{20, 40, 60\}\,cm, compared against Chain (results are normalized).}
	\label{fig:coalescing}
\end{figure}

We evaluate \sys experimentally to see its performance compared against Chain. Result is given in Figure~\ref{fig:coalescing}. For each application we measured execution time (with and without task coalescing) at \{20, 40, 60\}\,cm distance between RFID antenna and WISP and when WISP was powered directly from FET. Each measurement was for a predefined duration (each application was looping continuously) each distance/application case. From the result we clearly see an enormous benefit of \sys, especially at large WISP to RFID reader antenna distance. At each distance, \sys coalescing mechanism provided faster execution times compared to Chain.
